Topic Model

### 2021-08-26 manuscript/Partisan Media Manuscript.Rmd
graphs

@@

####make the table for study 1####
table1 = matrix(NA, ncol = 12, nrow = 23)
colnames(table1) = c("DV", "Mconservative", 
                     "SDconservative", "Mliberal", "SDliberal", 
                     "d", "dlow", "dhigh", "bcilowC", "bcihighC", 
                     "bcilowL", "bcihighL")
table1 = as.data.frame(table1)

####make the table for study 2: government shutdown####
table2 = matrix(NA, ncol = 12, nrow = 23)
colnames(table2) = c("DV", "Mconservative", 
                     "SDconservative", "Mliberal", "SDliberal", 
                     "d", "dlow", "dhigh", "bcilowC", "bcihighC", 
                     "bcilowL", "bcihighL")
table2 = as.data.frame(table2)

####make the table for study 2: Kavanaugh Hearings####
table3 = matrix(NA, ncol = 12, nrow = 23)
colnames(table3) = c("DV", "Mconservative", 
                     "SDconservative", "Mliberal", "SDliberal", 
                     "d", "dlow", "dhigh", "bcilowC", "bcihighC", 
                     "bcilowL", "bcihighL")
table3 = as.data.frame(table3)
```

@@

# Create IVs and DVs
groups = c(0, 1)
DVs = c('Analytic','Clout','Authentic','Tone','WPS','Sixltr','anger','social','family','female','male','cogproc','affiliation','achieve','power','reward','risk','focuspast','focuspresent','focusfuture','money','relig','death')

>>>>

Ever increasing attention is being paid to the impacts of partisanship on how people give and receive political information. The style and content of political information can be quantified in many ways, and one of those ways is motivation.

In the current study, we explore the motivations of partisan media coverage through the lens of McClelland's classic theory of motivation.

@@

####make the table for study 1####
table1 = matrix(NA, ncol = 12, nrow = 10)
colnames(table1) = c("DV", "Mconservative", 
                     "SDconservative", "Mliberal", "SDliberal", 
                     "d", "dlow", "dhigh", "bcilowC", "bcihighC", 
                     "bcilowL", "bcihighL")
table1 = as.data.frame(table1)

####make the table for study 2: government shutdown####
table2 = matrix(NA, ncol = 12, nrow = 10)
colnames(table2) = c("DV", "Mconservative", 
                     "SDconservative", "Mliberal", "SDliberal", 
                     "d", "dlow", "dhigh", "bcilowC", "bcihighC", 
                     "bcilowL", "bcihighL")
table2 = as.data.frame(table2)

####make the table for study 2: Kavanaugh Hearings####
table3 = matrix(NA, ncol = 12, nrow = 10)
colnames(table3) = c("DV", "Mconservative", 
                     "SDconservative", "Mliberal", "SDliberal", 
                     "d", "dlow", "dhigh", "bcilowC", "bcihighC", 
                     "bcilowL", "bcihighL")
table3 = as.data.frame(table3)
```

@@

# Create IVs and DVs
groups = c(0, 1)
DVs = c('i','you','shehe','we','they','ipron','affiliation','achieve','power')

### 2021-08-26 manuscript/topic_model.Rmd
updated with gamma
graphs

>>>>

# Interpretating Topics

- Topic 1: Trump Impeachment
- Topic 2: Immigration
- Topic 3: U.S.-China Relations
- Topic 4: Supreme Court
- Topic 5: Party Politics
- Topic 6: Military and Defense
- Topic 7: U.S-Russia Relations
- Topic 8: Technology
- Topic 9: Congress
- Topic 10: Campaign Scandals

```{r}
LDA_gamma <- as.data.frame(tidy(LDA_fit, matrix = "gamma"))
LDA_gamma <- reshape(LDA_gamma, idvar = 'document', timevar = 'topic', direction = 'wide')

DF$document <- row.names(DF)
LDA_topics <- merge(DF, LDA_gamma, by = 'document')
```

```{r}
library(sjPlot)
setwd('C:/Users/kayla/Documents/GitHub/Will-Pilot/manuscript/graphs')
LDA_topics$PartisanLean = as.factor(LDA_topics$PartisanLean)
# 1 = Conservative, 2 = Liberal (neg coeff = )
aff1 = glm(affiliation~gamma.1*PartisanLean, data = LDA_topics)
png('aff1.png')
plot_model(aff1, type='int')
dev.off()
pow1 = glm(power~gamma.1*PartisanLean, data = LDA_topics)
png('pow1.png')
plot_model(pow1, type='int')
dev.off()
ach1 = glm(achieve~gamma.1*PartisanLean, data = LDA_topics)
png('ach1.png')
plot_model(ach1, type='int')
dev.off()

aff2 = glm(affiliation~gamma.2*PartisanLean, data = LDA_topics)
png('aff2.png')
plot_model(aff2, type='int')
dev.off()
pow2 = glm(power~gamma.2*PartisanLean, data = LDA_topics)
png('pow2.png')
plot_model(pow2, type='int')
dev.off()
ach2 = glm(achieve~gamma.2*PartisanLean, data = LDA_topics)
png('ach2.png')
plot_model(ach2, type='int')
dev.off()

aff3 = glm(affiliation~gamma.3*PartisanLean, data = LDA_topics)
png('aff3.png')
plot_model(aff3, type='int')
dev.off()
pow3 = glm(power~gamma.3*PartisanLean, data = LDA_topics)
png('pow3.png')
plot_model(pow3, type='int')
dev.off()
ach3 = glm(achieve~gamma.3*PartisanLean, data = LDA_topics)
png('ach3.png')
plot_model(ach3, type='int')
dev.off()

aff4 = glm(affiliation~gamma.4*PartisanLean, data = LDA_topics)
png('aff4.png')
plot_model(aff4, type='int')
dev.off()
pow4 = glm(power~gamma.4*PartisanLean, data = LDA_topics)
png('pow4.png')
plot_model(pow4, type='int')
dev.off()
ach4 = glm(achieve~gamma.4*PartisanLean, data = LDA_topics)
png('ach4.png')
plot_model(ach4, type='int')
dev.off()

aff5 = glm(affiliation~gamma.5*PartisanLean, data = LDA_topics)
png('aff5.png')
plot_model(aff5, type='int')
dev.off()
pow5 = glm(power~gamma.5*PartisanLean, data = LDA_topics)
png('pow5.png')
plot_model(pow5, type='int')
dev.off()
ach5 = glm(achieve~gamma.5*PartisanLean, data = LDA_topics)
png('ach5.png')
plot_model(ach5, type='int')
dev.off()

aff6 = glm(affiliation~gamma.6*PartisanLean, data = LDA_topics)
png('aff6.png')
plot_model(aff6, type='int')
dev.off()
pow6 = glm(power~gamma.6*PartisanLean, data = LDA_topics)
png('pow6.png')
plot_model(pow6, type='int')
dev.off()
ach6 = glm(achieve~gamma.6*PartisanLean, data = LDA_topics)
png('ach6.png')
plot_model(ach6, type='int')
dev.off()

aff7 = glm(affiliation~gamma.7*PartisanLean, data = LDA_topics)
png('aff7.png')
plot_model(aff7, type='int')
dev.off()
pow7 = glm(power~gamma.7*PartisanLean, data = LDA_topics)
png('pow7.png')
plot_model(pow7, type='int')
dev.off()
ach7 = glm(achieve~gamma.7*PartisanLean, data = LDA_topics)
png('ach7.png')
plot_model(ach7, type='int')
dev.off()

aff8 = glm(affiliation~gamma.8*PartisanLean, data = LDA_topics)
png('aff8.png')
plot_model(aff8, type='int')
dev.off()
pow8 = glm(power~gamma.8*PartisanLean, data = LDA_topics)
png('pow8.png')
plot_model(pow8, type='int')
dev.off()
ach8 = glm(achieve~gamma.8*PartisanLean, data = LDA_topics)
png('ach8.png')
plot_model(ach8, type='int')
dev.off()

aff9 = glm(affiliation~gamma.9*PartisanLean, data = LDA_topics)
png('aff9.png')
plot_model(aff9, type='int')
dev.off()
pow9 = glm(power~gamma.9*PartisanLean, data = LDA_topics)
png('pow9.png')
plot_model(pow9, type='int')
dev.off()
ach9 = glm(achieve~gamma.9*PartisanLean, data = LDA_topics)
png('ach9.png')
plot_model(ach9, type='int')
dev.off()

aff10 = glm(affiliation~gamma.10*PartisanLean, data = LDA_topics)
png('aff10.png')
plot_model(aff10, type='int')
dev.off()
pow10 = glm(power~gamma.10*PartisanLean, data = LDA_topics)
png('pow10.png')
plot_model(pow10, type='int')
dev.off()
ach10 = glm(achieve~gamma.10*PartisanLean, data = LDA_topics)
png('ach10.png')
plot_model(ach10, type='int')
dev.off()
```
